### 2023-09-01 paper/sec-dis-pseudodata.tex
systematic wording and Eq.

For each independent source of systematic uncertainty, which in this analysis
consists of  $\delta E_\ell$, $\delta E_h $,
and $\delta\theta_\ell$, we 
quantify its impact at the event yield level
\be
\label{eq:event_yields_systematic_error}
\delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(i)} \, ,\quad
\delta_{\rm sys}^{(E_h)} N_{\rm ev}^{(i)}
\, ,\quad
\delta_{\rm sys}^{(\theta_\ell)} N_{\rm ev}^{(i)} \, ,\qquad i=1,\ldots,N_{\rm bin} \, ,
\ee
by extending the calculation delineated in Sect.~(\ref{sec:pseudo-data_generation}).
%
First, we generate a Monte Carlo set of events, denoted by $\mathcal{D}_0$,
composed by $N_{\rm mc} \approx 10^7$ samples and determine the assignment of each event
to a point in the $\lp x,Q^2,E_{\nu}\rp$ space.
%
By comparing $\mathcal{D}_0$ with the number of events as calculated by Eq.~(\ref{eq:event_yields_calculation}), 
we can normalize the sampled $\mathcal{D}_0$ distribution with a factor $\hat{f}$ to reproduce the expected yield.
%
We then take each event in $\mathcal{D}_0$ and smear it with Gaussian distributions whose variances are given by Table~\ref{tab:FPF_experiments} to produce a set of new samples $\{\mathcal{D}_k\}$.
%
The smeared events are subjected to the same DIS cuts from Eq.~(\ref{eq:DISconditions}) and acceptances from Table~\ref{tab:FPF_experiments}.
%
The bin assignment of the events in the smeared samples $\mathcal{D}_k$ will in general be different from those of the baseline sample $\mathcal{D}_0$.

We define the uncertainty associated
to a given systematic source, say $\delta E_\ell$,
to be the mean of the absolute difference between the number of events in this bin for the smeared samples $\{\mathcal{D}_k\}$ normalized to $\hat{f}$  and the central prediction for the number of events
$N_{\rm ev}^{(i)}$ as calculated from Eq.~(\ref{eq:event_yields_calculation}):
\be
\delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(i)} =\la \Big|  \hat{f} {N}^{(i)}_{E_\ell-{\rm smeared}} -N_{\rm ev}^{(i)}\Big|\ra \, .
\ee
Individual sources of systematic errors are treated as uncorrelated among them, and hence
by producing samples where only one source of error is varied at a time
we can determine the systematic errors, Eq.~(\ref{eq:event_yields_systematic_error}), in each bin
for each of the considered experiments.
%
This approach has the benefit that rescaling individual sources of systematic
uncertainties, say to assess the impact of improved detector performance,
becomes straightforward.

>>>>

For each independent source of systematic uncertainty, which in this analysis
consists of  $\delta E_\ell$, $\delta E_h $,
and $\delta\theta_\ell$, we 
quantify its impact at the event yield level
\be
\label{eq:event_yields_systematic_error}
\delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(i)} \, ,\quad
\delta_{\rm sys}^{(E_h)} N_{\rm ev}^{(i)}
\, ,\quad
\delta_{\rm sys}^{(\theta_\ell)} N_{\rm ev}^{(i)} \, ,\qquad i=1,\ldots,N_{\rm bin} \, ,
\ee
by extending the calculation delineated in Sect.~(\ref{sec:pseudo-data_generation}).
%
First, we generate a Monte Carlo set of events, denoted by $\mathcal{D}_0$,
composed by $N_{\rm mc} \approx 10^7$ samples and determine the assignment of each event
to a point in the $\lp x,Q^2,E_{\nu}\rp$ space.
%
We then take each event in $\mathcal{D}_0$ and smear it with Gaussian distributions whose variances are given by Table~\ref{tab:FPF_experiments} to produce a set of new samples $\{\mathcal{D}_k\}$.
%
The smeared events are subjected to the same DIS cuts from Eq.~(\ref{eq:DISconditions}) and acceptances from Table~\ref{tab:FPF_experiments}.
%
The bin assignment of the events in the smeared samples $\mathcal{D}_k$ will in general be different from those of the baseline sample $\mathcal{D}_0$.

We define the fractional uncertainty associated
to a given systematic source, say $\delta E_\ell$, for bin $i$
to be the mean of the absolute difference between the number of events in this bin for the smeared samples $\{\mathcal{D}_k\}$  and the number of events in this bin for ${\mathcal{D}_0}$:
\be
\delta_{\rm sys}^{(E_\ell)} =\la \left|  \frac{{N}^{(i)}_{E_\ell-{\rm smeared},k} -N_0^{(i)}}{N_0^{(i)}}\right|\ra \, .
\ee
Individual sources of systematic errors are treated as uncorrelated among them, and hence
by producing samples where only one source of error is varied at a time
we can determine the systematic errors, Eq.~(\ref{eq:event_yields_systematic_error}), in each bin
for each of the considered experiments.
%
This approach has the benefit that rescaling individual sources of systematic
uncertainties, say to assess the impact of improved detector performance,
becomes straightforward.
